---
title: "NES"
author: "David Kane"
date: "2/26/2020"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(report)
library(rstanarm)
library(report)
library(devtools)
library(ggplot2
        )
library(tidyverse)

load("nes.rda")
```

```{r clean_data}
# This data is a mess. Where is the code book? Is this real NES data or some bs
# made up sample? This is a really good place to write down some thoughts on
# this data and where it comes from. Take a look at ROAS, pages 141 -- 142.

# We are trying to explain partyid7, which is the party identification of each
# respondent. Can we treat this as continuous? I think that lower numbers mean
# more Democratic.

# real_ideo is missing a lot. Should we just get rid of those rows? Depends on
# the time period we care about . . .

x <- nes %>% 
  as_tibble() %>% 
  select(year, partyid7, real_ideo, race_adj, 
         age_discrete, educ1, female, income) %>% 
  drop_na() %>% 
  mutate(gender = as.factor(ifelse(female == 1, "female", "non-female"))) %>% 
  mutate(race = as.factor(case_when(race_adj == 1 ~ "White",
                                    race_adj == 2 ~ "Black",
                                    TRUE ~ "Other")))
  
```

```{r model_1, cache=TRUE}
# What is the relationship, if any, between partyid7 and female? We will treat
# partyid7 as a continuous variable for this exercise, even though it is a
# categorical variable with 7 levels. Recall that 1 means Strong Democrat, 2
# means Democrat and so on, finishing with 7 for Strong Republican.

fit_1 <- stan_glm(data = x, partyid7 ~ gender, refresh = 0)
```

```{r model_2, cache=TRUE}
# What about the relationship between race and party ID? Need to have created a
# factor variable, or at least a character variable.

fit_2 <- stan_glm(data = x, partyid7 ~ race, refresh = 0)
```


```{r model_3, cache=TRUE}
fit_3 <- stan_glm(data = x, partyid7 ~ real_ideo, refresh = 0)
```

## Model Results

Here is a nicely printed summary of my model results, showing the relationship between party ID, on a 1 through 7 scale, and ideology, also on a 1 through 7 scale. Although these are ordered categories, I treat both variables as continuous.

```{r show_the_model, comment=NA}
print(fit_3, detail = FALSE, digits = 2)
```

It isn't the best thing I could imagine. I really want to figure out a way to add a caption. But it will do for now. 

Instead of just printing the simple object, we could print its summary.


```{r show_the_model_summary, comment=NA}
print(summary(fit_3), detail = FALSE, digits = 2)
```

But that adds a bunch of junk, including run-off-the-page text. Maybe there are options in something like `print.stanmvreg()` which might be helpful. Has no one bothered to ask on RStudio Community?

```{r left_over, include=FALSE}
newtable <- x %>% 
  select(partyid7, gender, race, real_ideo) %>% 
  mutate(pred_gender = predict(fit_1, x)) %>% 
  mutate(pred_race = predict(fit_2, x)) %>% 
  mutate(pred_idea = predict(fit_3, x))

#%>% 
#  slice(8000:8010) # Interesting rows.

# How similar/different are these predictions?

# They look pretty similar with pred_ida being the best, but we're not certain it
# is doing a good job.

# How do we know if a prediction is good?

# How much do bad predictions differ?

# Think about penalty functions and decision-making.

```



```{r ggplot}

# look at relationship between gender, party_id, and prediction

df <- as.data.frame(newtable)

graphic1 <- ggplot(df, aes(pred_gender, partyid7, fill = gender)) +
  geom_jitter(alpha = .4)

graphic1

graphic2 <- ggplot(df, aes(pred_gender, partyid7, fill = gender)) +
  geom_boxplot()

graphic2

graphic3 <- ggplot(df, aes(pred_race, partyid7, fill = race)) +
  geom_boxplot()

graphic3

df2 <- df %>%
  group_by(real_ideo)

graphic4 <- ggplot(df, aes(group = real_ideo,pred_idea, partyid7, fill = real_ideo)) +
  geom_boxplot()

graphic4
```




```{r}
# Fit a model similar to that in Gelman for the whole period. Interpret the
# details of the model. And, yes, you will be seeing questions similar to this
# on the exam!


fit_4 <- stan_glm(data = df, partyid7  ~ gender + race + real_ideo, refresh = 0)
fit_4

# Now fit the model for a single year. The coefficient values are different!
# Which ones are true?

dfnew <- df %>%
  mutate(real_ideo1 = real_ideo-1)

fit_5 <- stan_glm(data = dfnew, partyid7  ~ gender + race + real_ideo1, refresh = 0)
fit_5


# goal is to explain what models means
# if your female voter who's african american, you have an idealogy of zero,
# even if you have ideaology of 1, and it can't start at zero, you still have
# the negative. Bc other coefficeints add on so much, it makes sense that it would have to be
# negative the predicted black ideaology for a female with that idealogy
# black female with an ideaology is zero. Would have change in intercept and scale,
# but not in the magnitude. Slope stayed the same, but it changed range.
# Their party id is now 1 what we are calling 1






# Let's do as ROAS does and fit the model for each year. Recall all your
# list-column tricks from Gov 1005.




# Once we have that collection of models. Can we make a plot which looks like at
# least one of the panes from page 142?


```

